Inferring cosmology from gravitational waves using non-parametric detector-frame mass distribution

### 2024-10-29 src/tex/ms.tex
[showyourwork] overleaf sync

We then perform the remaining steps similar to Sec.~\ref{sec:inference_multi}.
We set the bounds for $\kappa$ to $[-10, 10]$, and the bounds for other free parameters are the same as in Table~\ref{tab:bounds}.
The result of the remapping is shown in Fig.~\ref{fig:real_result_multi}, and it is consistent with the posterior distribution reported in \cite{KAGRA:2021duu}.
\begin{figure}
    \script{plot_real_result_multi.py}
    \includegraphics[width=\linewidth]{figures/real_result_multi.pdf}
    \caption{
        Optimized parameter distribution for the real data inference.
    }
    \label{fig:real_result_multi}
\end{figure}
The result implies that \variable{output/real_H0.txt}, which has an uncertainty much smaller than $H_0 = 50^{+37}_{-30}$ reported in \cite{KAGRA:2021duu}.
This is mainly because the uncertainty only includes the uncertainty from the reconstruction, which underestimates the true uncertainty which also includes the mismatch between the population model and the observed population distribution.

>>>>

We then perform the remaining steps similar to Sec.~\ref{sec:inference_multi}.
We set the bounds for $\kappa$ to $[-10, 10]$, and the bounds for other free parameters are the same as in Table~\ref{tab:bounds}.
The result of the remapping is shown in Fig.~\ref{fig:real_result_multi}, and it is consistent with the posterior distribution reported in \cite{KAGRA:2021duu}.
\begin{figure}
    \script{plot_real_result_multi.py}
    \includegraphics[width=\linewidth]{figures/real_result_multi.pdf}
    \caption{
        Optimized parameter distribution for the real data inference.
    }
    \label{fig:real_result_multi}
\end{figure}

The result implies that \variable{output/real_H0.txt}, with symmetric $90\%$-credible intervals around the median.
The uncertainty is much smaller than the one reported in \cite{KAGRA:2021duu} ($H_0 = 50^{+37}_{-30} \, \mathrm{km/s/Mpc}$), mainly because it only includes the uncertainty from the reconstruction, which underestimates the true uncertainty which also includes the mismatch between the population model and the observed population distribution.
